The Impact of Educational Expenses of New Coders

### 2021-04-24 outputs/paper/paper.Rmd
Edit text in paper.Rmd

In the earlier section, I ran a correlation matrix to identify the correlation of each variable and the significance of the relationship between the dependent variable (MoneyForLearning) and other dependents variables. But, I was not able to estimate how much the independent variables impact the dependent variable from the correlation analysis. In this section, I will examine effects of the dependent variables on the dependent variable, focusing on one of the dependent variables: Income. The two main questions that I set out to answer in this section are: (1) How do beginner programmers' income affect the cost of their education to learn code? and (2) Will the effects change according to the population of the city where they live in. To obtain the answer for the first question, I used a simple linear regression model (Equation \@ref(eq:linRegModel1)) and multiple linear regression models (Equation \@ref(eq:linRegModel2) and \@ref(eq:linRegModel3)). All these three models use MoneyForLearning (the cost of their education to learn code) as a dependent variable. Model 1 contains only one independent variable, which is Income (see Equation \@ref(eq:linRegModel1)); otherwise, Model 3 uses all the independent options except for CommuteTime: Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree (see Equation \@ref(eq:linRegModel3)). As mentioned in the Correlation Analysis section, the CommuteTime (a commuting time) variable does not significantly affect the response variable, so it is excluded from the regression models. And, Model 2 uses the same independent variables, excluding Gender and Age. For the second question about the effects of the population of the city where the programmers reside, I used four simple linear regression models (see Equation \@ref(eq:linRegModel2)). Like Model 1, all these models use MoneyForLearning as a dependent variable and Income as an independent variable (see Equation \@ref(eq:linRegModel1)). But, the observations were grouped by the population size of the programmers. Model 4 contains any size of population; and Model 5,6, and 7 are the small (less than 100,000), medium (between 100,000 and 1 million), and large (more than 1 million) size population.

@@

>>>>

In the earlier section, I ran a correlation matrix to identify the correlation of each variable and the significance of the relationship between the dependent variable (MoneyForLearning) and other dependents variables. But, I was not able to estimate how much the independent variables impact the dependent variable from the correlation analysis. In this section, I will examine effects of the dependent variables on the dependent variable, focusing on one of the dependent variables: Income. The two main questions that I set out to answer in this section are: (1) How do beginner programmers' income affect the cost of their education to learn code? and (2) Will the effects change according to the population of the city where they live in.

To obtain the answer for the first question, I used a simple linear regression model (Equation \@ref(eq:linRegModel1)) and multiple linear regression models (Equation \@ref(eq:linRegModel2) and \@ref(eq:linRegModel3)). All these three models use MoneyForLearning (the cost of their education to learn code) as a dependent variable. Model 1 contains only one independent variable, which is Income (see Equation \@ref(eq:linRegModel1)); otherwise, Model 3 uses all the independent options except for CommuteTime: Gender, Age, CityPopulation, Income, MonthsProgramming, and SchoolDegree (see Equation \@ref(eq:linRegModel3)). As mentioned in the Correlation Analysis section, the CommuteTime (a commuting time) variable does not significantly affect the response variable, so it is excluded from the regression models. And, Model 2 uses the same independent variables, excluding Gender and Age. For the second question about the effects of the population of the city where the programmers reside, I used four simple linear regression models (see Equation \@ref(eq:linRegModel2)). Like Model 1, all these models use MoneyForLearning as a dependent variable and Income as an independent variable (see Equation \@ref(eq:linRegModel1)). But, the observations were grouped by the population size of the programmers. Model 4 contains any size of population; and Model 5,6, and 7 are the small (less than 100,000), medium (between 100,000 and 1 million), and large (more than 1 million) size population.

@@

As explained in the Data section, categorical variables were converted to continuous variables for the linear regression models. For example, the SchoolDegree variable (the level of education) was a categorical variable with character values. So, I converted the variable into a variable with numeric values, using the `dplyr` package. A complete list of survey questions and response options for each question can be found in the Appendix. Since the MoneyForLearning variable (the level of education) was not only categorical but also ordered and ranked in the original dataset, I converted the variable into a variable with numeric values. Also, I merged some of the response options of the variable. For instance, it is somewhat hard to say that a high school diploma or equivalent (GED) is higher than trade, technical, or vocational training, and a professional degree, such as MBA, MD, or JD, is higher than a non-professional master's degree. So, I merged the options, using the `recode` function of the `dplyr` package [@cityDplyr].
